VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper_background.tex
re

\begin{figure}[htb]
    \centering
    %\includegraphics[width=3in]{images/colocated-arch}
    \includegraphics[width=3in]{images/converged_arch}
    \caption{VM snapshot backup running on a converged cloud cluster.}
    \label{fig:collocated}
\end{figure}

@@

Index sampling with a prefetch cache  is proposed in
in~\cite{Guo2011} for efficient single-machine deduplication. 
This scheme uses 25GB memory per 500TB of raw data
and thus the ratio is 20K:1. Our scheme proposed in this paper 
uses 4 times less memory and we have not incorporated this index 
sampling technique because its extension for
for a distributed architecture is difficult.  To use a distributed memory version 
of the sampled index, every deduplication
request may access a remote machine for index lookup and the overall overhead 
of access latency for all requests can be significant.

>>>>

\begin{figure}[htb]
    \centering
    %\includegraphics[width=3in]{images/colocated-arch}
    \includegraphics[width=3.25in]{images/converged_arch}
    \caption{VM snapshot backup running on a converged cloud cluster.}
    \label{fig:collocated}
\end{figure}

@@

Index sampling with a prefetch cache  is proposed in
in~\cite{Guo2011} for efficient single-machine deduplication. 
This scheme uses 25GB memory per 500TB of raw data
and thus the raw data to memory ratio is 20K:1. Our scheme proposed in this paper 
uses three times less memory and we have not incorporated this index 
sampling technique because its extension for
for a distributed architecture is difficult.  To use a distributed memory version 
of the sampled index, every deduplication
request may access a remote machine for index lookup and the overall overhead 
of access latency for all requests can be significant.
